Evaluation of the article

### 2024-11-18 pages/paper_evaluation.qmd
feat(paper evaluation): alternative scores and relationship with reproduction

```{python}
import pandas as pd
from functions import eval_chart, plot_scatter

@@

Of the applicable criteria, all studies fully met at least 60% (and many others still partially met).

I don't think we learn much in relation to items reproduced, and that it is more interesting to consider which criteria were met and whether this aided the reproduction or not.

*Note. This plots the proportion of **applicable** criteria that were **fully met***.

```{python}
plot_scatter('STRESS-DES criteria met',
             sho = (17/24)*100,
             hua = (14/23)*100,
             lim = (15/21)*100,
             kim = (15/22)*100,
             ana = (14/21)*100,
             joh = (16/19)*100,
             her = (18/23)*100,
             woo = (22/24)*100)
```

@@

The proportion of applicable criteria met was lower for this checklist.

However, I again think it's most relevant to consider which criteria were met, rather than draw conclusions from this chart.

*Note. This plots the proportion of **applicable** criteria that were **fully met***.

```{python}
plot_scatter('ISPOR-SDM criteria met',
             sho = (11/15)*100,
             hua = (7/16)*100,
             lim = (12/16)*100,
             kim = (12/17)*100,
             ana = (8/15)*100,
             joh = (15/17)*100,
             her = (10/17)*100,
             woo = (13/17)*100)
```

>>>>

```{python}
import pandas as pd
import plotly.express as px
from functions import eval_chart, plot_scatter, calculate_scores

@@

Of the applicable criteria, all studies fully met at least 60% (and many others still partially met) (`score_fully`).

Looking at the quality score suggested (`score`), we see no relationship between reporting quality and reproduction sucess. This remains the case when using other scoring systems used in other papers (`score_schwander` and `score_zhang`).

```{python}
def check_reporting(df):
  '''
  Check the reporting quality of each study with different scoring systems

  Parameters:
  -----------
  df : pandas dataframe
    Dataframe with counts of fully, partially, not met and na items
  '''
  # Add reproduction success
  df['reproduce'] = [94, 37.5, 100, 100, 100, 80, 12.5, 100]

  # Calculating some reporting quality scores
  scores = calculate_scores(df).rename_axis('study').reset_index()
  display(scores)

  # Plot relationship of score with reproduction success
  for score in ['score', 'score_fully', 'score_schwander', 'score_zhang']:
    fig = px.scatter(scores, x=score, y='reproduce', hover_data={'study': True})
    fig.update_layout(xaxis_range=[-10, 110],
                      yaxis_range=[-10, 110],
                      yaxis_title='Items reproduced',
                      xaxis_ticksuffix='%',
                      yaxis_ticksuffix='%')
    fig.show()

check_reporting(stress_wide)
```

@@

The proportion of applicable criteria met was lower for this checklist (`score_fully`).

Same conclusions as for STRESS.

```{python}
check_reporting(ispor_wide)
```
